---
title: "2017 grad student course survey results"
author: "Rick Gilmore"
date: "`r Sys.time()`"
output: 
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      error = FALSE)

require(tidyverse)
```

# Purpose

This document summarizes the results of a survey of Psychology Department graduate students conducted in 2017. It concerns the quantitative methods courses they have taken, and wish to have offered in the future.

# Plan

1. Import the data
2. Clean it, as necessary
2. Visualize the data

# Import and clean

```{r}
quant_surv_df <- readr::read_csv("csv/quant_course_survey-2017-clean.csv")
str(quant_surv_df)
```

# Visualize {.tabset}

## Top courses taken

```{r}
quant_surv_df %>%
  dplyr::select(., Course, Took_psy, Took_oth) %>%
  dplyr::mutate(., Took_total = Took_psy + Took_oth) %>%
  dplyr::filter(., Took_total > 0) %>%
  dplyr::arrange(., desc(Took_total)) %>%
  knitr::kable(., format = "html", escape = FALSE) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  kableExtra::scroll_box(width="800px")
```

## Top courses desired

The following table calculates a `Most_popular` variable equal to `Offer_reg + Offer_summ - Offer_no` then sorts on it.

```{r}
quant_surv_df %>%
  dplyr::mutate(., Most_popular = Offer_reg + Offer_summ - Offer_no) %>%
  dplyr::mutate(., Offer_total = Offer_reg + Offer_summ) %>%
  dplyr::filter(., Offer_total > 0) %>%
  dplyr::arrange(., desc(Offer_total)) %>%
  dplyr::select(.,
                Course,
                Offer_reg,
                Offer_summ,
                Offer_total,
                Offer_no,
                Most_popular,
                Status) %>%
  dplyr::mutate(., Status = kableExtra::cell_spec(Status,
                                                  'html', color = ifelse(
                                                    Status == "Not_offered",
                                                    "red",
                                                    ifelse(Status %in% c("2022"), "green", "orange")
                                                  ))) %>%
  knitr::kable(., format = "html", escape = FALSE) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  kableExtra::scroll_box(width = "800px")
```
